Paper Results Section

### 2019-03-26 notebooks/corpus_stats_and_plots.Rmd
notebooks, new plots, data up to date. still debating if i should push it ... it big

r_counts <- readRDS("../data/R_loc_by_package.RDS")
c_counts <- readRDS("../data/c_loc_by_package.RDS")

@@

@@

plot_both <- plot_both + theme(
  axis.text.x  = element_blank(), 
  axis.title.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.ticks.y = element_line(), 
  panel.grid.major.y = element_line(colour = "red")) + # ,
  # panel.ontop = T) + 
  scale_y_continuous(name="Lines of Code in Package", breaks = c(-4, -3, -2, -1, 0, 1, 2, 3, 4), 
                     labels = c(10000, 1000, 100, 10, 0, 10, 100, 1000, 10000))
  # geom_line(aes( x, y), cut_top) +
  # geom_line(aes( x, y), cut_bot)

@@

Changing gears, lets get the number of recorded events by package.
Final numbers will become available as the trace completes.
```{r}

records_by_fun <- unlist(readRDS("../data/total_list_of_records_by_pkg.RDS"))
records_by_fun_df <- data.frame(pname=names(records_by_fun), records=unname(records_by_fun)/1000)
# records_by_fun_df <- records_by_fun_df[order(records_by_fun_df$records), ]
# records_by_fun_df$pname <- factor(records_by_fun_df$pname, levels=records_by_fun_df$pname)

plot_records <- ggplot(data=records_by_fun_df, aes(x=pname, y=records, group=1)) +
                geom_line() + 
                labs( title = "Numbers of Recorded Signatures",
                      y = "Recorded Traces in a Package (Thousands)") +
                theme(axis.text.x = element_blank(), axis.title.x=element_blank(),
                      axis.ticks.x=element_blank())

>>>>

count_df <- readRDS("../data/final_loc_counts.RDS")

r_counts <- count_df[, 1]; names(r_counts) <- rownames(count_df)
c_counts <- count_df[, 2]; names(c_counts) <- rownames(count_df)

# for observations
records_by_fun <- readRDS("../data/final_obs_counts_df.RDS")
pkgs_to_plot <- intersect(rownames(records_by_fun), names(r_counts))

r_counts <- r_counts[pkgs_to_plot]
c_counts <- c_counts[pkgs_to_plot]
records_by_fun[ "pkg" ] <- rownames(records_by_fun) # needed for plotting

records_by_fun <- records_by_fun[records_by_fun[,"pkg"] %in% pkgs_to_plot, ]

top_10 <- c("Rcpp", "rlang", "glue", "tibble", "stringi", "ggplot2", "dplyr", "pillar", "R6", "stringr")

@@

loc_of_top_10 <- lapply(1:length(combo_df$package_name), function(x) if (combo_df$package_name[[x]] %in% top_10) x else FALSE)

@@

plot_both <- plot_both + theme(
  axis.text.x  = element_blank(), 
  axis.title.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.ticks.y = element_line(), 
  panel.grid.major.y = element_line(colour = "red")) + # ,
  # panel.ontop = T) + 
  scale_y_continuous(name="Lines of Code in Package", breaks = c(-4, -3, -2, -1, 0, 1, 2, 3, 4), 
                     labels = c(10000, 1000, 100, 10, 0, 10, 100, 1000, 10000)) # +
  # scale_x_discrete(name="Package", breaks = unlist(loc_of_top_10[!(loc_of_top_10 == FALSE)]), labels = top_10)
  # geom_line(aes( x, y), cut_top) +
  # geom_line(aes( x, y), cut_bot)

@@

Plot:
```{r}

records_by_fun$pkg <- factor(records_by_fun$pkg, levels=combo_df$package_name)
# log scale?
records_by_fun$invo_obs <- sapply(records_by_fun$invo_obs, function(x) if (x == 0) x else log10(x))

plot_records <- ggplot(data=records_by_fun, aes(x=pkg, y=invo_obs, group=1)) +
                geom_line(size=0.25) + 
                labs( title = "Numbers of Observed Signatures",
                      y = "Observed Invocations in Pkg (Thousands, log10-Scaled)") +
                theme(axis.text.x = element_blank(), axis.title.x=element_blank(),
                      axis.ticks.x=element_blank()) +
                scale_y_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6), 
                     labels = c(0, 10, 100, 1000, 10000, 100000, 1000000))

### 2019-03-26 notebooks/paper_results_section.Rmd
notebooks, new plots, data up to date. still debating if i should push it ... it big

Load the data.
```{r, echo=FALSE}
los <- list.files("../data/full_sigs", full.names=TRUE)
names <- list.files("../data/full_sigs")
names(los) <- substr(names, 1, nchar(names)-4)
los <- lapply(los, readRDS)
los <- remove_empties(los)
# annoying strange error that I should fix pops up
```

@@

```{r}
tot_arg_df <- data.frame(
  Type=c("Full Monomorphic", "Monomorphic in Type", "Monomorphic in Class", "Monomorphic in Attribute Pattern", "Total Seen"),
  Count=c(total_mono_all, total_mono_type, total_mono_clas, total_mono_attr, total_arguments),
  Percentage=round(c(total_mono_all, total_mono_type, total_mono_clas, total_mono_attr, total_arguments) / total_arguments * 100, 2)
)

@@

```{r}
tot_fun_df <- data.frame(
  Type=c("Full Monomorphic", "Monomorphic in Type", "Monomorphic in Class", "Monomorphic in Attribute Pattern", "Total Seen"),
  Count=c(total_mono_all_functions, total_mono_type_functions, total_mono_clas_functions, total_mono_attr_functions, total_functions),
  Percentage=round(c(total_mono_all_functions, total_mono_type_functions, total_mono_clas_functions, total_mono_attr_functions, total_functions) / total_functions * 100, 2)
)

@@

We Have one thing we want to do first.
Namely, let's get rid of vector/X, scalar/X polymorphism.
```{r}
los_vs <- lapply(los, function(lofuns) {lapply(lofuns, combine_scalar_vector_where_appropriate)})
```

@@

Print top 10.
```{r}
format_df_for_print(poly_type_args[1:10,]) -> put_me
xtable(put_me)
```

Now, having noted that:
(1) vector/X, scalar/X is common, and
(2) ints and doubles are basically interchangable
while noting that together these make up a huge portion of the polymorphism, we transform.
```{r}

```

>>>>

Load the data.
```{r, echo=FALSE}
los <- list.files("../data/full_sigs", full.names=TRUE)
names <- list.files("../data/full_sigs")
names(los) <- substr(names, 1, nchar(names)-4)
los <- lapply(los, readRDS)
los <- remove_empties(los)
# annoying strange error that I should fix pops up

# There's at least one transformation that we're always gonna want to apply, namly the vector/scalar
# collapse where both are present in a signature.
los <- lapply(los, function(lofuns) {lapply(lofuns, combine_scalar_vector_where_appropriate)})
```

@@

```{r}
tot_arg_df <- data.frame(
  Type=c("Full Monomorphic", "Monomorphic in Type", "Monomorphic in Class", "Monomorphic in Attribute Pattern", "Total Seen"),
  Count=round(c(total_mono_all, total_mono_type, total_mono_clas, total_mono_attr, total_arguments) / 1000, 0),
  Percentage=round(c(total_mono_all, total_mono_type, total_mono_clas, total_mono_attr, total_arguments) / total_arguments * 100, 2)
)

@@

```{r}
tot_fun_df <- data.frame(
  Type=c("Full Monomorphic", "Monomorphic in Type", "Monomorphic in Class", "Monomorphic in Attribute Pattern", "Total Seen"),
  Count=round(c(total_mono_all_functions, total_mono_type_functions, total_mono_clas_functions, total_mono_attr_functions, total_functions) / 1000, 0),
  Percentage=round(c(total_mono_all_functions, total_mono_type_functions, total_mono_clas_functions, total_mono_attr_functions, total_functions) / total_functions * 100, 2)
)

@@

@@

Print top 10.
```{r}
format_df_for_print(poly_type_args[1:10,]) -> put_me
put_me
xtable(put_me)
```

Now, having noted that:
(1) ints and doubles are basically interchangable, and
(2) null and NA should be a part of every type,
while also noting that together these make up a huge portion of the polymorphism, we transform.
```{r}
los <- lapply(los, function(s) lapply(s, fold_NULL_and_NA_into_other_types_df))
null_na_fold_arg_counts <- build_arg_count_df_from_lopkgs(los)
null_na_fold_fun_counts <- build_fun_count_df_from_lopkgs(los)

los <- lapply(los, function(lof) {lapply(lof, function(df) {change_type_systems_df(df, type_map_sv_to_real)})})
null_na_fold_real_arg_counts <- build_arg_count_df_from_lopkgs(los)
null_na_fold_real_fun_counts <- build_fun_count_df_from_lopkgs(los)
```
